\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-29 manuscript/manuscript.tex
quick comments

\section{Appendix}\label{sec:appendix}
In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block bootstrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of
block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block} and \ref{fig:large_block}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$ and $\Gamma(8,1)$.
  }
  \label{fig:large_block}
\end{figure}

Even for the settings with block sizes that are typically less than
$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
algorithm still does not hold its size as demonstrated in 
Figure~\ref{fig:my_setting}, and the block
sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
considered optimal in general.

@@

@@

@@

\item[Data availability statement:] The data and code used in the real data analysis and simulation
studies are publicly available in a GitHub repo:
\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

>>>>

\appendix

\section{Block Size Investigation}\label{sec:appendix}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block}
  \caption{Proportion of selected block sizes using the method of
  \citet{politis2004automatic} that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$ and $\Gamma(8,1)$.
  }
  \label{fig:large_block}
\end{figure}
In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block bootstrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.
\jy{add discussions about the figure}

@@

Even for the settings with block sizes that are typically less than
$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
algorithm still does not hold its size as demonstrated in 
Figure~\ref{fig:my_setting}, and the block
sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
considered optimal in general.
\jy{How do you interpret the flat lines in the plot? Why are the
  empirical cdf step functions? That means your empirical p-values are
  discrete with point masses at a few points. Check the p-values from
  the simulations.}

@@

\jy{Discuss the figure}

@@

\item[Data availability statement:] The data and code used in the real data analysis and simulation
studies are publicly available in a GitHub repo:\\
\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.
